Enhancing Adversarial Robustness for Deep Metric Learning

### 2021-10-30 robdml.tex
tex

To figure out the efficacy of HM with $H_\mathcal{D}$ calculated from benign
triplets, we adversarialy train models dataset using $\text{HM}[\mathcal{R},
\mathcal{M}]$ and $\text{HM}[\mathcal{S}, \mathcal{M}]$ on the CUB dataset,
with varying PGD steps, \ie, $\eta\in\{2,4,8,16,32\}$, respectively.
%
The results can be found in \cref{tab:hmeff}.
%
The performance of the state-of-the-art defense, \ie, ACT~\cite{robrank} is
also provided as a baseline.
%
ACT[$\mathcal{R}$] and ACT[$\mathcal{S}$] mean the training
triplet is sampled using Random and Softhard strategy, respectively.
%

@@

\begin{figure}[t]
	\includegraphics[width=\columnwidth]{fighmeff.pdf}
	\caption{HM eff}
\end{figure}

>>>>

To figure out the efficacy of HM with $H_\mathcal{D}$ calculated from benign
triplets, we adversarialy train models dataset using $\text{HM}[\mathcal{R},
\mathcal{M}]$ and $\text{HM}[\mathcal{S}, \mathcal{M}]$ on the CUB dataset,
with varying PGD steps, \ie, $\eta\in\{2,4,8,16,32\}$, respectively.
%
The results can be found in \cref{tab:hmeff}.
%
The performance of the state-of-the-art defense, \ie, ACT~\cite{robrank} is
also provided as a baseline.
%
ACT[$\mathcal{R}$] and ACT[$\mathcal{S}$] mean the training triplet is sampled
using Random and Softhard strategy, respectively.
%
We also plot curves in \cref{fig:hmeff} based on the robustness, training
cost~\footnote{Training cost is the number of forward-backward computation
cycle in each adversarial training iteration, and is calculated as $\eta+1$.},
as well as the R@1 performance on benign examples to reflect the
characteristics of these methods.

@@

\begin{figure}[t]
	\includegraphics[width=\columnwidth]{fighmeff.pdf}
	\caption{HM eff}
	\label{fig:hmeff}
\end{figure}
